\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
..

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)
	The programming model for Oak is that each packet entering the network is mapped to a forwarding decision that describes where the packet should end up leaving the network. For simplicity, we assume that we are targeting a one big switch implementation of the network. The one big switch model has been heavily optimized \cite{Obs}, and we view the problem of determining paths through the network as orthogonal to our work here.

@@

The rest of the API, included in Figure~\ref{fig:build_api}, consists of functions used to interact with Red Oak. \lstinline|compile| is used to trace a policy from a given function from packet to forwarding \lstinline|decision|. \lstinline|run| simulates the compiled \lstinline|policy| on a series of \lstinline|examples|. In the remainder of this section, we describe these functions in more detail.

>>>>

   \subsection*{Forwarding Decision}
   % can give constant decision (e.g. drop() or fwd(loc) to a certain location loc), or decision based on values of the packet (e.g. deliver() which forwards to dst)
	The programming model for \textit{Red Oak} is that each packet entering the network is mapped to a forwarding decision that describes where the packet should end up leaving the network. For simplicity, we assume that we are targeting a one big switch implementation of the network. The one big switch model has been heavily optimized \cite{Obs}, and we view the problem of determining paths through the network as orthogonal to our work here.

@@

The rest of the API, included in Figure~\ref{fig:build_api}, consists of functions used to interact with \textit{Red Oak}. \lstinline|compile| is used to trace a policy from a given function from packet to forwarding \lstinline|decision|. \lstinline|run| simulates the compiled \lstinline|policy| on a series of \lstinline|examples|. In the remainder of this section, we describe these functions in more detail.
